Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2019-10-05 manuscript/manuscript.tex
edits

While it challenging to apply temporal methods to natural populations there is
a lot of promise for these approaches
\parencite{Bergland2014-ij,Machado2018-cs}. Efforts to estimate the quantify
the impact of linked selection in have suggested a 19\% to 89\% \vb{reduction
in genome-wide diversity} over long time periods is driven by \vb{linked
selection}
\parencite{McVicker2009-ax,Elyashiv2016-vt,Corbett-Detig2015-gt,Coop2016-gx,Comeron2014-nh}
Thus there is reason to be hopeful that we could detect this from temporal
data, which would help to resolve the timescales that linked selection act
over. In our reanalysis of the \textcite{Barghi2019-qy} study, we find evidence
of complex linked selection dynamics, with selection pressures flipping over
time due to either environmental change, the breakup of epistatic combinations
or advantageous haplotypes. Such patterns would be completely obscured in
samples only from contemporary populations, thus we can hope to have a much
richer picture of linked selection as temporal sequencing becomes more common,
\vb{perhaps allowing us to observe the effects of ecological dynamics in
genomic data \parencite{Hairston2005-ga}.}

>>>>

While it challenging to apply temporal methods to natural populations there is
a lot of promise for these approaches
\parencite{Bergland2014-ij,Machado2018-cs}. Efforts to estimate the quantify
the impact of linked selection in have \gc{found over obligately
  sexual origanisms SHOULD WE SAY 0-89} 19\% to 89\% \vb{reduction
in genome-wide diversity} over long time periods is driven by \vb{linked
selection}
\parencite{McVicker2009-ax,Elyashiv2016-vt,Corbett-Detig2015-gt,Coop2016-gx,Comeron2014-nh}
Thus there is reason to be hopeful that we could detect this from temporal
data, which would help to resolve the timescales that linked selection act
over. In our reanalysis of the \textcite{Barghi2019-qy} study, we find evidence
of complex linked selection dynamics, with selection pressures flipping over
time due to either environmental change, the breakup of epistatic combinations
or advantageous haplotypes. Such patterns would be completely obscured in
samples only from contemporary populations, thus we can hope to have a much
richer picture of linked selection as temporal sequencing becomes more common,
\vb{perhaps allowing us to observe the effects of ecological dynamics in
genomic data \parencite{Hairston2005-ga}.}
